Constraining the Interiors of Asteroids Through Close Encounters

### 2022-08-03 paper/appendices.tex
Orientation data set fit process

\subsection{Uncertainty model}
We will use the same tools to extract data from the orientation data set as we did in the main text for the angular velocity data set. The only item that requires redefinition is the likelihood used by the MCMC (equation \ref{eqn:log-likelihood}), which depends on a model for the uncertainty of orientation observations.

>>>>

We may expect some differences in the resolving power of orientation and angular velocity data, but not a large difference, due to the following argument. If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment. Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid position. The initial position is defined up to $\gamma_0$ by the assumption of no initial tumbling, and figures \ref{fig:scan-physical} and \ref{fig:scan-observational} reveal that $\gamma_0$ is typically also constrained to high precision even by angular velocity data. Thus, we expect the only differences between moment uncertainty as obtained from angular velocity data or from orientation data to be due to the uncertainty of the data itself.

\subsection{Uncertainty model}
The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data. This requires a new model for the uncertainty of orientation observations.
